### 2020-06-30 Documents/ESA/sections/ResearchSummary.tex
Added Missing Reference in Appendix

	We are now ready to take the expectation of $Q$. To do this, we will exploit the fact that the
	payoff elements are Gaussian distributed and use the identity \cite{QFTbook}

@@

We will evaluate the path integral using the saddle point method for integration 
\cite{saddlepoint}. In this method, we consider that the integration is dominated by the maximum of
the function

>>>>

	We are now ready to take the expectation of $Q$. To do this, we will exploit the fact that the
	payoff elements are Gaussian distributed and use the identity \cite{ZinnJustin2009}

@@

We will evaluate the path integral using the saddle point method for integration. In this method, we consider that the integration is dominated by the maximum of
the function
